Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-12 ms.qmd
writs some methods about GAMMs

@@

   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + habitat + type + type:habitat + s(long.x, lat.y, by = habitat) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)

@@

#pred <- posterior_epred(model5_bayes, re_formula = 'NA')

>>>>

#### Modelling how climate change will impact on opportunity for selection

To understand the consequences of human-induced climate change on the potential to impact the opportunity for selection on physiogical traits we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude. We assumed that any change in $lnCVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat). We used cubic splines for latitude and longitude (and their interaction) as any response could be complicated by local factors. Our model included random effects of species, trait, phylogeny and study. We predcited the expected change in $lnCVR_{Q_{10}}$ for each wild population in our dataset at the specific populations latitude and longitude.

@@

   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + habitat + type + type:habitat + t2(long.x, lat.y, by = habitat) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)

@@

pred <- conditional_smooths(model5_bayes)
pp_check(model5_bayes)
```
